Davos: a Python package ``smuggler'' for constructing lightweight reproducible notebooks

### 2023-07-13 paper/main.tex
edits through section 2.1

The Davos package consists of two interdependent subpackages
(see Fig.~\ref{fig:package-structure}). The first,
\texttt{davos.core}, comprises a set of modules that
implement the bulk of the package's core
functionality, including pipelines for installing and validating
packages, custom parsers for the \texttt{smuggle} statement (see
Sec.~\ref{subsec:smuggle}) and onion comment (see
Sec.~\ref{subsec:onion}), and a runtime interface for configuring
Davos's behavior (see Sec.~\ref{subsec:config}). However,
certain critical aspects of this
functionality require (often substantially) different implementations
depending on properties of the notebook environment in which
Davos is used (e.g., whether the frontend is provided by
Jupyter or Google Colaboratory, or which version of
IPython~\cite{PereGran07} is used by the notebook kernel). To deal
with this, environment-dependent parts of core features and behaviors
are isolated and abstracted to ``helper functions'' in the
\texttt{davos.implementations} subpackage. This second subpackage
defines multiple, interchangeable versions of each helper function,
organized into modules by the conditions that trigger their use. At
runtime, Davos detects various features in the notebook
environment and selectively imports a single version of each helper
function into the top-level \texttt{davos.implementations} namespace,
allowing \texttt{davos.core} modules to access the proper
implementations for the current notebook environment in a single,
consistent location. An additional benefit of this design is that it
allows maintainers, developers, and users to extend Davos to
support new, updated, or custom notebook variants by creating new
\texttt{davos.implementations} modules that define their own versions
of each helper function, modified from existing implementations as
needed.

>>>>

The Davos package consists of two interdependent subpackages
(see Fig.~\ref{fig:package-structure}). The first,
\texttt{davos.core}, comprises a set of modules that
implement the bulk of the package's core
functionality, including pipelines for installing and validating
packages, custom parsers for the \texttt{smuggle} statement (see
Sec.~\ref{subsec:smuggle}) and onion comment (see
Sec.~\ref{subsec:onion}), a system for isolating dependencies of
different projects (see Sec.~\ref{subsec:projects}), and a runtime
interface for configuring Davos's behavior (see Sec.~\ref{subsec:config}).
However, certain critical aspects of this
functionality require (often substantially) different implementations
depending on properties of the notebook environment in which
Davos is used (e.g., whether the frontend is provided by
Jupyter or Google Colaboratory, or which version of
IPython~\cite{PereGran07} is used by the notebook kernel). To deal
with this, environment-dependent components of core features and behaviors
are isolated and abstracted to ``helper functions'' in the
\texttt{davos.implementations} subpackage. This second subpackage
defines multiple, interchangeable versions of each helper function,
organized into modules by the conditions that trigger their use. At
runtime, Davos detects various features in the notebook
environment and selectively imports a single version of each helper
function into the top-level \texttt{davos.implementations} namespace,
allowing \texttt{davos.core} modules to access the proper
implementations for the current notebook environment in a single,
consistent location. An additional benefit of this design is that it
allows maintainers, developers, and users to extend Davos to
support new, updated, or custom notebook variants by creating new
\texttt{davos.implementations} modules that define their own versions
of each helper function, modified from existing implementations as
needed.
